|

### 2024-08-08 doc/paper.qmd
table 1 replication

>>>>

Now that it is clear that the number of observations for this project is significantly higher than that in @Leuz_2003 study, in order to illustrate the differences and compare the firm-year observations, Table 1 from @Leuz_2003 was partially replicated (only columns on countries and firm/year observations) to distinguish specific discrepancies that could arise for certain countries. The following table representes the (partially) replicated Table 1.
